Offshore Indices of Abundance for <br/> Blue Crabs

### 2020-01-08 2019_edits/R/offshore_analyses/crabs_per_hectare.Rmd
offshore analysis report

---
title: "Offshore Crabs/Hectare Modeling"
editor_options: 
  chunk_output_type: console
---
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

**Overall Mean Catch Crabs/Hectare: `r overall_mean`**
**Stations with no catch: `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`**

@@

Percent Deviance for model 1a. = `r perc_dev`

@@

Percent Deviance for model 1a. = `r perc_dev`

>>>>

---0
title: "Offshore Indices of Abundance for <br/> Blue Crabs"
author: "Adam A Kemberling"
date: "1/4/2020"
output: 
  html_document:
    toc: true
    toc_float: true
editor_options: 
  chunk_output_type: console
---

@@

**Overall Mean Catch Crabs/Hectare:** `r overall_mean`

**Stations with no catch:** `r percent_zeros` / `r station_count` or `r (percent_zeros / station_count) * 100`

@@

Percent Deviance for model A. = `r perc_dev`

@@

Percent Deviance for model B. = `r perc_dev`
